
```{r specific-wave-specific-analyses-1, include=FALSE}
safeRequire('data.tree');
safeRequire('treemap');
```

<!-- ### Where participants expect a first-aid -->

### Expected first-aid competence

```{r specific-wave-specific-analyses-first-aid-competence}

tmpPlot <- ggEasyBar(dat, grep('estimatedCompetenceL_', names(dat), value=TRUE),
                     labels=labelDf[grep('estimatedCompetenceL_', labelDf$varNames.cln), 'subQuestions'],
                     xlab=NULL, ylab=NULL,
                     showInLegend="none", fontColor=NA) +
             scale_y_continuous(breaks=seq(0, 100, 10)) +
             theme(legend.position="none",
                   text=element_text(size=26),
                   plot.background = element_rect(fill = "transparent",
                                                  color = NA),
                   panel.grid = element_blank(),
                   axis.ticks.x = element_line(size=1),
                   axis.ticks.length=unit(1, 'line'));

ggSave(plot=tmpPlot,
       file.path(workingPath,
                 "estimatedCompetenceL-ggEasyBar.png"),
       width=16,
       height=4,
       bg = "transparent");

knitFig(tmpPlot,
        figWidth  = 16,
        figHeight = 4,
        figCaption = "estimatedCompetenceL-ggEasyBar");
  
tmpPlot <- ggEasyBar(dat, grep('estimatedCompetenceS_', names(dat), value=TRUE),
                     labels=labelDf[grep('estimatedCompetenceS_', labelDf$varNames.cln), 'subQuestions'],
                     xlab=NULL, ylab=NULL,
                     showInLegend="none", fontColor=NA) +
             scale_y_continuous(breaks=seq(0, 100, 10)) +
             theme(legend.position="none",
                   text=element_text(size=26),
                   plot.background = element_rect(fill = "transparent",
                                                  color = NA),
                   panel.grid = element_blank(),
                   axis.ticks.x = element_line(size=1),
                   axis.ticks.length=unit(1, 'line'));

ggSave(plot=tmpPlot,
       file.path(workingPath,
                 "estimatedCompetenceS-ggEasyBar.png"),
       width=16,
       height=4,
       bg = "transparent");

knitFig(tmpPlot,
        figWidth  = 16,
        figHeight = 4,
        figCaption = "estimatedCompetenceS-ggEasyBar");

```

### Intention to visit the first aid

```{r specific-wave-specific-analyses-2}

dat$faFriendNoUse_intention <- ifelse(dat$faFriend_RandomSelect == "noUseMention",
                                      dat$faFriend_intention,
                                      NA);
dat$faFriendOtherUsed_intention <- ifelse(dat$faFriend_RandomSelect == "otherUsed",
                                          dat$faFriend_intention,
                                          NA);
dat$faFriendUsedSelf_intention <- ifelse(dat$faFriend_RandomSelect == "usedSelf",
                                         dat$faFriend_intention,
                                         NA);

intentionVars <- grep('_intention', names(dat), value=TRUE);
intentionVars <- grep('faFriend_intention', intentionVars, value=TRUE, invert=TRUE);

tmpPlot <- 
  meansDiamondPlot(dat,
                   items=rev(intentionVars),
                   labels=rev(c("... with a light complaint",
                                "... with an alcohol-related complaint",
                                "... with a substance-related complaint",
                                "... if a friend doesn't feel well\nand substance use is not mentioned",
                                "... if a friend doesn't feel well\nand that friend used a substance",
                                "... if a friend doesn't feel well\nand the participant used a substance")),
                   conf.level=.9999,
                   xbreaks=1:7,
                   generateColors = c("red", "green"),
                   fullColorRange = c(1,7),
                   xlab="Participants' intention scores and 99.99 confidence intervals for the means") +
    labs(title="Intention to visit a nightlife first aid site in different situations",
         caption="(1 = Absolutely not, 7 = Absolutely)") +
  theme(legend.position="none",
        text=element_text(size=26),
        plot.background = element_rect(fill = "transparent",
                                       color = NA));

ggSave(plot=tmpPlot,
       file.path(workingPath,
                 "visitFirstAid_intention-diamondPlot-English.png"),
       width=18,
       height=8,
       bg = "transparent");

knitFig(tmpPlot,
        figWidth=18,
        figHeight=8,
        figCaption = "visitFirstAid_intention-diamondPlot-English");

tmpPlot <-
  meansDiamondPlot(dat,
                   items=rev(intentionVars),
                   labels=rev(c("... met een lichte klacht",
                                "... met een alcohol-gerelateerde klacht",
                                "... met een drugs-gerelateerde klacht",
                                "... als een vriend(in) zich niet goed voelt\nen middelengebruik niet wordt genoemd",
                                "... als een vriend(in) zich niet goed voelt\nen drugs heeft gebruikt",
                                "... als een vriend(in) zich niet goed voelt\nen de deelnemer drugs heeft gebruikt")),
                   conf.level=.9999,
                   xbreaks=1:7,
                   generateColors = c("red", "green"),
                   fullColorRange = c(1,7),
                   xlab="Intenties en 99.99% betrouwbaarheidsintervallen voor de gemiddelden") +
  labs(title="Intentie om de eerste hulp in het nachtleven te bezoeken",
       caption="(1 = Absoluut niet, 7 = Absoluut)") +
  theme(legend.position="none",
        text=element_text(size=26),
        plot.background = element_rect(fill = "transparent",
                                       color = NA));

ggSave(plot=tmpPlot,
       file.path(workingPath,
                 "visitFirstAid_intention-diamondPlot-Dutch.png"),
       width=18,
       height=8,
       bg = "transparent");

knitFig(tmpPlot,
        figWidth=18,
        figHeight=8,
        figCaption = "visitFirstAid_intention-diamondPlot-Dutch");

```

### Whether visiting the first aid ruins the evening

```{r specific-wave-specific-analyses-single-beliefs-1}

tmpPlot <- ggEasyBar(dat, grep('AttExpect1_ruinsEvening', names(dat), value=TRUE),
                     labels=c("Met een vriend(in)", "Met een lichte klacht", "Met een alcohol-klacht", "Met een drugs-klacht"),
                     xlab=NULL, ylab=NULL,
                     showInLegend="none", fontColor=NA) +
             scale_y_continuous(breaks=seq(0, 100, 10)) +
             theme(legend.position="none",
                   text=element_text(size=26),
                   plot.background = element_rect(fill = "transparent",
                                                  color = NA),
                   panel.grid = element_blank(),
                   axis.ticks.x = element_line(size=1),
                   axis.ticks.length=unit(1, 'line'));

ggSave(plot=tmpPlot,
       file.path(workingPath,
                 "AttExpect1_ruinsEvening-ggEasyBar.png"),
       width=16,
       height=4,
       bg = "transparent");

knitFig(tmpPlot,
        figWidth  = 16,
        figHeight = 4,
        figCaption = "AttExpect1_ruinsEvening-ggEasyBar");

```

### Whether access to the party is denied after visiting the first aid

```{r specific-wave-specific-analyses-single-beliefs-2}

### labelDf[labelDf$varNames.cln == "faSelfSubstAttExpect2_accessToParty", ];

tmpPlot <- ggEasyBar(dat, grep('accessToParty', names(dat), value=TRUE),
                     labels=c("Met een vriend(in)", "Met een lichte klacht", "Met een alcohol-klacht", "Met een drugs-klacht"),
                     xlab=NULL, ylab=NULL,
                     showInLegend="none", fontColor=NA) +
             scale_y_continuous(breaks=seq(0, 100, 10)) +
             theme(legend.position="none",
                   text=element_text(size=26),
                   plot.background = element_rect(fill = "transparent",
                                                  color = NA),
                   panel.grid = element_blank(),
                   axis.ticks.x = element_line(size=1),
                   axis.ticks.length=unit(1, 'line'));

ggSave(plot=tmpPlot,
       file.path(workingPath,
                 "accessToParty-ggEasyBar.png"),
       width=16,
       height=4,
       bg = "transparent");

knitFig(tmpPlot,
        figWidth  = 16,
        figHeight = 4,
        figCaption = "accessToParty-ggEasyBar");
  
```

### Entactogen preference ('deserted island' scenario)

```{r specific-wave-specific-analyses-3, results='asis'}

entactoFreqs <- freq(dat$entactogenPreference);

pander(entactoFreqs);

```

`r paste0("So,", entactoFreqs$dat['none', 'Perc.Valid'], " percent prefers to bring nothing.");`

```{r specific-wave-specific-analyses-4, fig.width=14, fig.height=10, fig.cap="Treemap of entactogen preferences", warning=FALSE, message=FALSE, error=FALSE}

entactoNamesRaw <- entactoFreqs$intermediate$categoryNames;
entactoProportions <- entactoFreqs$intermediate$frequencies.prop.valid;

entactoNames <- gsub('75', '075', entactoNamesRaw);
entactoNames <- gsub('md(.*)', 'MDMA powder,\n\\1mg', entactoNames);
entactoNames <- gsub('x(.*)', 'XTC pills,\n\\1mg', entactoNames);
entactoNames <- gsub('fa(.*)', '4-FA,\n\\1mg', entactoNames);
entactoNames <- ifelse(entactoNames=='none', 'z', entactoNames);

entactoOrderFull <- order(entactoNames);

entactoNames <- ifelse(entactoNames=='z', 'None', entactoNames);

entactoNames <- paste0(entactoNames, " (", round(100*entactoProportions), "%)");

#entactoOrder <- order(entactoNames);

entactoNames <- entactoNames[entactoOrderFull];
entactoProportions <- entactoProportions[entactoOrderFull];

entactoDataframe <- data.frame(entactoNames, entactoProportions);

entactoDataframe$Name <- gsub("(.*) \\(.*\\)", "\\1", entactoDataframe$entactoNames);
entactoDataframe$Dose <- gsub("(.*) \\((.*)\\)", "\\2", entactoDataframe$entactoNames);
entactoDataframe$SubstanceNr <- as.numeric(factor(entactoDataframe$Name));
entactoDataframe$entactoOrder <- 1:nrow(entactoDataframe);

entactoDataframe$pathString <- paste0("Substance/", entactoDataframe$Name, "/", entactoDataframe$Dose);
#entactoDataframe

entactoTree <- as.Node(entactoDataframe);

entactoDataframe$color <-
  c(rep("#2A5581", 4),
    rep("#172F47", 4),
    rep("#CBDDEE", 4),
    "#999999");

treemap(entactoDataframe,
        title="Preferences for XTC, MDMA powder, and 4-FA",
        index='entactoNames',
        vSize='entactoProportions',
        vColor='color',
        type='color',
        algorithm='pivotSize',
        sortID='entactoOrder',
        fontsize.labels=35,
        fontsize.title=40,
        draw=TRUE);

png(file.path(workingPath, "forced choice 4-fa treemap.png"),
   type='cairo-png', height=1400, width=2000);
treemap(entactoDataframe,
        title="Preferences for XTC, MDMA powder, and 4-FA",
        index='entactoNames',
        vSize='entactoProportions',
        vColor='color',
        type='color',
        algorithm='pivotSize',
        sortID='entactoOrder',
        fontsize.labels=35,
        fontsize.title=40,
        draw=TRUE);
dev.off();

```

### Reasons for their 'desert island' preference

Note that these are in Dutch.

```{r specific-wave-specific-analyses-5, results='asis'}
 
for (entactoPref in 1:length(entactoNamesRaw)) {
  cat("\n\n##### ", gsub('\\n', ' ', entactoNames[entactoPref]),
      "\n\n");
  cat(paste0("- ", dat$entactoGenPrefWhy,
             " `(intentions to use XTC=", dat$substUseIntention_xtc,
             ", MDMA=", dat$substUseIntention_mdma,
             ", 4-FA=", dat$substUseIntention_fourf,
             "; use in past 6 months of XTC=", dat$substUseFreq_xtc,
             ", MDMA=", dat$substUseFreq_mdma,
             ", 4-FA=", dat$substUseFreq_fourfa,
             ")` \n")[(dat$entactogenPreference == entactoNamesRaw[entactoOrderFull][entactoPref]) & !is.na(dat$entactoGenPrefWhy)]);
}

```

